%-----------------------------------------------------
%  Introduction
%-----------------------------------------------------

\section{Introduction}
Artificial muscles have been vastly studied in Robotics to perform human's delicate movements \cite{ashley}. Recently, a super-coiled polymer(SCP) artificial muscle and its striking features were discovered by Haines \etal \cite{haines} The \scp is a new kind of artificial muscles which can be easily fabricated by simply twisting a nylon thread excessively. This artificial muscle contracts when heated while it relaxes when cooled.

It is known \scps can provide fast, nonhysteretic, strong, and large stroke at low costs\cite{yuan, mirvakili, madden}. 
Since the \scp was announced in 2014, it has been widely studied in many different fields, such as its application on
wearable robots \cite{sphincter, kianzad2}, 
anthropomorphic robotic hands \cite{yip, finger}, 
and modeling of its mechanism \cite{treatise, torsional, youngmodulus, fab_coil, multiscale, healing, kianzad, moretti}. 
%However, appropriate circumstances for SCP artificial muscle%, especially cooling device, 
%hadn't been studied enough to apply this artificial muscle into real robots.
However, the \scps have failed to be examined in appropriate circumstances enough to apply these artificial muscles into real robots.

Haines \etalspace present \scpnospace's heating method - fabricating the \scps with silver coated nylon thread and applying electric current, which provides Joule heat to muscles \cite{haines}. This method was checked and applied by several works \cite{yip, mirvakili,kianzad,sphincter,kianzad2}. However, methods for cooling \scps have been largely unsuccessful to date. 
Although water flow has been tried many times \cite{haines,finger},
it causes \scps not to last for a long time \cite{haines}.
%and it is hard to be applied to robots. 
Furthermore, the application of the process to robots is rather difficult.
%Also, cooling fan was used in Yip \etal, but it didn't get sufficiently fast cooling speed.
Yip \etalspace also used a cooling fan in their study \cite{yip}, but it couldn't obtain sufficiently fast cooling speed.
% Thermo Neslab cc65 immersion cooler in \cite{kianzad}
% Liquid Nitrogen in Ionov.
% 'Electrical heating combined with compressed air or water for cooling are natural choices in the operating room. : Madden2015 : `Twisted Lines

In this paper, \antanospace, which is actuated by two complementarily contracting \scpsnospace, was assembled and its operating system was attached. Also, behaviors of the \scps and \anta were simply modeled with linear equations and tested experimentally. By quantifying thermal conductivity, possibility of feedback cooling was confirmed. In conclusion, algorithms for the sustainable \apc were designed, performed, and simulated.